---
title: "Parameterized Analysis"
author: "Ashutosh Nandeshwar"
date: "`r Sys.Date()`"
output: html_document
params:
  inp_species: "Adelie"
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = TRUE)
```

## Load Libraries and Data
We will use sample data from the `palmerpenguins` package. The data contains information about penguins.

```{r loadlibs}
library(palmerpenguins)
library(tidyverse)
library(summarytools)
library(viridis)
library(ggthemes)
library(gt)
library(gtsummary)
```

## Filter Data for a Species
Let's filter the data for a **`r params$inp_species`** species.

Top 5 rows of the filtered data:

```{r filterdata}
penguins_filtered <- penguins %>% 
  filter(species == params$inp_species)

head(penguins_filtered) %>% gt
```

## Linear regression model
Let's build a linear regression model to predict body mass based on flipper length,  bill length and bill depth.

```{r linregmodel}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm +  bill_length_mm, penguins_filtered)

summary(model_1)

tbl_regression(model_1)
```

<!-- ## Models for every island -->
<!-- Let's build a linear regression model for each island. -->

<!-- ```{r linregmodelisland, results='asis'} -->

<!-- for (this_island in unique(penguins_filtered$island)) { -->
<!--   cat(paste0("### Island: ", this_island, "\n")) -->
<!--   penguins_filtered_island <- penguins_filtered %>%  -->
<!--     filter(island == this_island) -->

<!--   this_model <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm +  bill_length_mm, penguins_filtered_island) -->

<!--   print(tbl_regression(this_model)) -->

<!--   cat("\n\n") -->
<!-- } -->
<!-- ``` -->


<!-- do not uncomment here. Rmarkdown won't knit. run all species -->
<!-- for (sp in unique(penguins$species)) {
  render(
    input = "03_parameterized_analysis.Rmd",
    output_file = paste0(sp, "_analysis.html"),
    params = list(inp_species = sp)
  )
} -->
